---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r}
library(ggplot2)
library(classdata)

## import Ames Data
data("ames")
str(ames)
summary(ames)
dim(ames)

```

1.  Inspect the first few lines of the data set:

-   what variables are there? of what type are the variables? what does each variable mean? what do we expect their data range to be?

    -   There are 16 variables in this data sets

        1.  Parcel ID, character, character with ID. It doesn't have the range.

        2.  Address, character, property address in Ames, IA. It doesn't have the range.

        3.  Style, factor variable, factor variable detailing the type of housing. It doesn't have the range.

        4.  Occupancy, factor variable, factor variable of type of housing. It doesn't have the range.

        5.  Sale Date, date, date of sale. Range: 2017-07-03 - 2022-08-31.

        6.  Sale Price, number, sales price (in US dollar), Range: 0 \$ - 20500000\$

        7.  Multi Sale, logical value: was this sale part of a package. It doesn't have the range.

        8.  YearBuilt, Integer, year in which the house was built. Range: 0 - 2022.

        9.  Acres, integer, amount of acres of land. Range: 0-13

        10. Total living area, Sqf of living area. Range 0-6007

        11. Bedrooms, num of bedrooms. Range 0-10

        12. FinishedBsmntArea, Sqf of finished basemnet. Range 10-6500.

        13. LotArea, Sqf of lot size. Range 0-524,000

        14. AC, whether there is AC or not. Yes or No

        15. Fireplace, whether there is a Fireplace or not. Yes or No

        16. Neighborhood, what neighborhood its in, Factor with 42 options

    ```{r}


    ```
